### 2015-11-30 fundamentals/intro.tex
line 102 -- added 'and facility types'

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community to achieve two important goals: lower the
barrier for users to include custom nuclear technologies in their fuel cycle
analyses while improving the ability to compare simulations with and without
those custom concepts.  This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives.  While the \emph{modular and open architecture} of
\Cyclus is necessary to meet these goals, it is not sufficient.
\emph{Agent interchangeability} is also required to facilitates direct comparison
of alternative modeling methodologies and facility concepts. With this concept
at its core, \Cyclus provides a platform for users to quickly develop the
capabilities at a level of detail and validation necessary for their
unique applications.  Finally, \Cyclus is applicable to a broader range of
fidelities, scales, and applications than other simulators, due to the
flexibility and generality of its \emph{\gls{ABM}} paradigm and \emph{discrete,
object-oriented approach}.

>>>>

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community to achieve two important goals: lower the
barrier for users to include custom nuclear technologies and facility types in 
their fuel cycle
analyses while improving the ability to compare simulations with and without
those custom concepts.  This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives.  While the \emph{modular and open architecture} of
\Cyclus is necessary to meet these goals, it is not sufficient.
\emph{Agent interchangeability} is also required to facilitates direct comparison
of alternative modeling methodologies and facility concepts. With this concept
at its core, \Cyclus provides a platform for users to quickly develop the
capabilities at a level of detail and validation necessary for their
unique applications.  Finally, \Cyclus is applicable to a broader range of
fidelities, scales, and applications than other simulators, due to the
flexibility and generality of its \emph{\gls{ABM}} paradigm and \emph{discrete,
object-oriented approach}.
